### 2010-02-17 trunk/deliverables/D5_1_1/fast_d5_1_1.tex
changes to Internationalisation section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@564 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 19/02/2010 & Ciprian Palaghita (Cyntelix) & First version of the deliverable \\
 & & Ismael Rivera (NUIG) & \\ \hline
\end{tabular}
\end{small}

@@

\singlespacing
\begin{verbatim}
{
  "label": {
    "en-GB": "Product Search",
    "es-ES": "Ejemplo Sencillo",
    "de-DE": "Produktsuche"
  },
  "description": {
    "en-GB": "On this screen, the user can enter a search term.",
    "es-ES": "Esto es un ejemplo sencillo de pantalla",
    "de-DE": "Auf diesem Screen kann der Benutzer einen Suchbegriff eingeben."
  },
}
\end{verbatim}
\doublespacing

\singlespacing
\begin{verbatim}
<rdf:Description rdf:about="http://www.morfeoproject.eu/fast/fco#ExampleScreen">
  <rdf:type rdf:resource="http://www.morfeoproject.eu/fast/fco#Screen"/>
  <rdfs:label xml:lang="en-GB">Simple Example</rdfs:label>
  <rdfs:label xml:lang="es-ES">Ejemplo Sencillo</rdfs:label>
  <rdfs:label xml:lang="de-DE">Einfaches Beispiel</rdfs:label>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="en-GB">This is a simple example of a screen</description>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="es-ES">Esto es un ejemplo sencillo de pantalla</description>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="de-DE">Dies ist ein einfaches Beispiel für einen Bildschirm</description>
</rdf:Description>
\end{verbatim}
\doublespacing

Until now, using internationalisation is allowed for the label and the description of a screen, but in the near future, more attributes will benefit from this feature.

>>>>

\begin{small}
\begin{tabular}{|l|l|l|p{6.6cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 19/02/2010 & Ciprian Palaghita (Cyntelix) & First version of the deliverable \\
 & & Ismael Rivera (NUIG) & \\ \hline
\end{tabular}
\end{small}

@@

\singlespacing
\begin{verbatim}
{
  "label": {
    "en-GB": "Product Search",
    "es-ES": "Búsqueda de productos",
    "de-DE": "Produktsuche"
  },
  "description": {
    "en-GB": "On this screen, the user can enter a search term.",
    "es-ES": "En esta ventana, el usuario puede introducir el criterio de búsqueda",
    "de-DE": "Auf diesem Screen kann der Benutzer einen Suchbegriff eingeben."
  }
}
\end{verbatim}
\doublespacing

\singlespacing
\begin{verbatim}
<rdf:RDF
    xmlns:rdf="http://www.w3.org/1999/02/22-rdf-syntax-ns#"
    xmlns:foaf="http://xmlns.com/foaf/0.1/"
    xmlns:dc="http://purl.org/dc/terms/"
    xmlns:fgo="http://purl.oclc.org/fast/ontology/gadget#"
    xmlns:xsd="http://www.w3.org/2001/XMLSchema#"
    xmlns:rdfs="http://www.w3.org/2000/01/rdf-schema#"
    xmlns:ctag="http://commontag.org/ns#">
  <rdf:Description rdf:about="http://demo.fast.morfeo-project.org/FASTCatalogue/screens/1">
    <rdf:type rdf:resource="http://purl.oclc.org/fast/ontology/gadget#Screen"/>
    <rdfs:label xml:lang="en-gb">Product Search</rdfs:label>
    <rdfs:label xml:lang="en-es">Búsqueda de productos</rdfs:label>
    <rdfs:label xml:lang="en-de">Produktsuche</rdfs:label>
    <dc:description xml:lang="en-gb">On this screen, the user can enter a search
    term.</dc:description>
    <dc:description xml:lang="en-gb">En esta ventana, el usuario puede introducir
    el criterio de búsqueda.</dc:description>
    <dc:description xml:lang="en-gb">Auf diesem Screen kann der Benutzer einen
    Suchbegriff eingeben.</dc:description>
  </rdf:Description>
</rdf:RDF>
\end{verbatim}
\doublespacing

Internationalisation is being used by the attributes \emph{label} and \emph{description} of any building block, \emph{label} of the pre/postconditions and \emph{label} of the tags.
